KidsAIR initial home/child data work

### 2019-12-18 dustrak_data_cleaning.Rmd
PM data cleaning

---
title: "KidsAIR initial PM data work"
author: "Ethan Walker"
date: "Started 19 Nov 2019, Updated 16 Dec 2019"
output: pdf_document
---

@@

```{r, message=FALSE}
library(tidyverse)
library(readxl)
library(naniar)
library(lubridate)
library(zoo)
```

@@

# Change function input to look at specific home
# Run all of these lines together
pm_time_plot_function(id = "512", location = "WMT")
head(gaps, 25)
head(pm_desc, 25)
tail(pm_desc, 25)

# filter data for a single home
check_data <- kids_pm %>% 
  filter(area == "AK" & home_winter_id == "10")

@@

>>>>

---
title: "KidsAIR initial PM data work"
author: "Ethan Walker"
date: "Started 19 Nov 2019, Updated 18 Dec 2019"
output: pdf_document
---

@@

```{r, message=FALSE}
library(tidyverse)
library(readxl)
library(naniar)
library(lubridate)
library(zoo)
jvPalette <- c("#330099","#CC0066","#FF6633", 
                 "#0099CC", "#FF9900","#CC6633",
                  "#FF3366", "#33CC99", "#33999")
```

@@

# Change function input to look at specific home
# Run all of these lines together
pm_time_plot_function(id = "140", location = "NN")
head(gaps, 25)
head(pm_desc, 25)
tail(pm_desc, 25)

# filter data for a single home
check_data <- kids_pm %>% 
  filter(area == "NN" & home_winter_id == "140")

@@

# Fix dusttrak sample start times
```{r}
# Load data
kids_pm <- read_rds("Output/kids_pm_new.rds")

# Checking difference between dustrak start datetime and field data log datetime
sample_times <- kids_pm %>% 
  #filter(area == "NN") %>% 
  group_by(area, home_winter_id) %>% 
  arrange(pm_datetime) %>% 
  unite(start_datetime, c("startdate", "starttime"), 
        sep = " ", remove = FALSE) %>% 
  mutate(first_datetime = first(pm_datetime),
         first_datetime = ymd_hms(first_datetime),
         start_datetime = ymd_hms(start_datetime),
         time_diff = first_datetime - start_datetime) %>% 
  #distinct(time_diff, .keep_all = TRUE) %>% 
  # make general time changes based on ranges
  mutate(pm_datetime = ymd_hms(pm_datetime),
         pm_datetime_new = if_else(time_diff > 1800 & time_diff < 5400, 
                                   pm_datetime - 3600, pm_datetime),
         pm_datetime_new = if_else(time_diff < -1800 & time_diff > -5400, 
                                   pm_datetime_new + 3600, pm_datetime_new),
         pm_datetime_new = if_else(time_diff > 5400 & time_diff < 9000, 
                                   pm_datetime_new - 7200, pm_datetime_new),
         pm_datetime_new = if_else(time_diff < -5400 & time_diff > -9000, 
                                   pm_datetime_new + 7200, pm_datetime_new)) %>% 
  # make specific time changes
  mutate(pm_datetime_new = if_else(time_diff == 10903, # WMA457
                                   pm_datetime_new - 10800, pm_datetime_new),
         pm_datetime_new = if_else(time_diff == (-82721), # WMA440
                                   pm_datetime_new + 82800, pm_datetime_new),
         pm_datetime_new = if_else(time_diff == 10069, # WMA459
                                   pm_datetime_new - 9900, pm_datetime_new),
         pm_datetime_new = if_else(time_diff == 9817, # WMA314
                                   pm_datetime_new - 3600, pm_datetime_new),
         pm_datetime_new = if_else(time_diff < -31535900, # YKC06-103 
                                   pm_datetime_new + 31539519, pm_datetime_new),
         pm_datetime_new = if_else(time_diff < -31532200, # WMA305
                                   pm_datetime_new - 3600, pm_datetime_new),
         pm_datetime_new = if_else(time_diff == 9120, # WMA228
                                   pm_datetime_new - 3600, pm_datetime_new),
         pm_datetime_new = if_else(time_diff == (-21497), # WMA130
                                   pm_datetime_new + 21497, pm_datetime_new),
         pm_datetime_new = if_else(time_diff == 684, # WMA237
                                   pm_datetime_new + 3600, pm_datetime_new),
         pm_datetime_new = if_else(time_diff == 149793, # WMA238
                                   pm_datetime_new - 149793, pm_datetime_new),
         pm_datetime_new = if_else(time_diff == -46227, # CH320
                                   pm_datetime_new + 3600, pm_datetime_new),
         pm_datetime_new = if_else(time_diff == 13514, # TC360 
                                   pm_datetime_new - 3600, pm_datetime_new),
         pm_datetime_new = if_else(time_diff == -10696, # TC357 
                                   pm_datetime_new + 10800, pm_datetime_new),
         pm_datetime_new = if_else(time_diff == -43427, # TC355 
                                   pm_datetime_new + 43200, pm_datetime_new),
         pm_datetime_new = if_else(time_diff == -11388, # TC353 
                                   pm_datetime_new + 10800, pm_datetime_new),
         pm_datetime_new = if_else(time_diff == -221, # TC351 
                                   pm_datetime_new + 3600, pm_datetime_new)) %>% 
  mutate(first_datetime_new = first(pm_datetime_new),
         first_datetime_new = ymd_hms(first_datetime_new),
         start_datetime = ymd_hms(start_datetime),
         time_diff_new = first_datetime_new - start_datetime) %>% 
  distinct(time_diff, .keep_all = TRUE)

```

### 2019-12-18 home_child_data_cleaning.Rmd
PM data cleaning

---
title: "KidsAIR initial home/child data work"
author: "Ethan Walker"
date: "Started 19 Nov 2019, Updated 16 Dec 2019"
output: pdf_document
---

@@

# Load, format, and save home and child overview/demographic data for WMT
```{r}
# Load files
wmt_child_initial <- read_xlsx("Input/WMT/wmt_child_20191126.xlsx") %>% 
  rename_all(tolower) %>% 
  select(childid, homeid, id, hispanic, race, agenov1, enrolled) %>% 
  mutate(child_id_num = as.character(childid),
         home_id = as.character(homeid),
         child_id_char = as.character(id),
         hispanic_child = as.factor(hispanic),
         race_child = as.factor(race),
         age_child_nov = as.character(agenov1)) %>% 
  select(child_id_num, home_id, child_id_char, hispanic_child,
         race_child, age_child_nov, enrolled)

wmt_home_initial <- read_xlsx("Input/WMT/wmt_home_20191126.xlsx") %>% 
  rename_all(tolower) %>% 
  select(homeid, home, txcondition) %>% 
  mutate(home_id = as.character(homeid),
         home = as.character(home),
         treatment = as.factor(txcondition)) %>% 
  select(home_id, home, treatment)

wmt_homewinter_initial <- read_xlsx("Input/WMT/wmt_homewinter_20191126.xlsx") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, homeid, winterid, interventiondate, interventiontime) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         home_id = as.character(homeid),
         winter_id = as.character(winterid),
         intervention_date = interventiondate,
         intervention_time = interventiontime) %>% 
  select(home_winter_id, home_id, winter_id, intervention_date, intervention_time)

wmt_parent_demographics_initial <-
  read_xlsx("Input/WMT/wmt_parent_demographics_20191126.xlsx") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, gender, hispanic, race, income, education,
         totalres, underfive) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         gender_parent = as.factor(gender),
         hispanic_parent = as.factor(hispanic),
         race_parent = as.factor(race),
         income = as.factor(income),
         education = as.factor(education),
         total_residents = as.character(totalres),
         residents_under_five = as.character(underfive)) %>% 
  select(home_winter_id, gender_parent, hispanic_parent, race_parent,
         income, education, total_residents, residents_under_five) %>% 
  filter(!is.na(gender_parent))

@@

# Load, format, and save home and child overview/demographic data for NN
```{r}
# Load files
nn_child_initial <- read_xlsx("Input/NN/nn_child_20191216.xlsx") %>% 
  rename_all(tolower) %>% 
  select(childid, homeid, id, hispanic, race, agenov1, enrolled) %>% 
  mutate(child_id_num = as.character(childid),
         home_id = as.character(homeid),
         child_id_char = as.character(id),
         hispanic_child = as.factor(hispanic),
         race_child = as.factor(race),
         age_child_nov = as.character(agenov1)) %>% 
  select(child_id_num, home_id, child_id_char, hispanic_child,
         race_child, age_child_nov, enrolled)

nn_home_initial <- read_xlsx("Input/NN/nn_home_20191216.xlsx") %>% 
  rename_all(tolower) %>% 
  select(homeid, home, txcondition) %>% 
  mutate(home_id = as.character(homeid),
         home = as.character(home),
         treatment = as.factor(txcondition)) %>% 
  select(home_id, home, treatment)

nn_homewinter_initial <- read_xlsx("Input/NN/nn_homewinter_20191216.xlsx") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, homeid, winterid, interventiondate, interventiontime) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         home_id = as.character(homeid),
         winter_id = as.character(winterid),
         intervention_date = interventiondate,
         intervention_time = interventiontime) %>% 
  select(home_winter_id, home_id, winter_id, intervention_date, intervention_time)

nn_parent_demographics_initial <-
  read_xlsx("Input/NN/nn_parent_demographics_20191216.xlsx") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, gender, hispanic, race, income, education,
         totalres, underfive) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         gender_parent = as.factor(gender),
         hispanic_parent = as.factor(hispanic),
         race_parent = as.factor(race),
         income = as.factor(income),
         education = as.factor(education),
         total_residents = as.character(totalres),
         residents_under_five = as.character(underfive)) %>% 
  select(home_winter_id, gender_parent, hispanic_parent, race_parent,
         income, education, total_residents, residents_under_five) %>% 
  filter(!is.na(gender_parent))

@@

# Load, format, and save home and child overview/demographic data for AK
```{r}
# Load files
ak_child_initial <- read_xlsx("Input/AK/ak_child_20191216.xlsx") %>% 
  rename_all(tolower) %>% 
  select(childid, homeid, id, hispanic, race, agenov1, enrolled) %>% 
  mutate(child_id_num = as.character(childid),
         home_id = as.character(homeid),
         child_id_char = as.character(id),
         hispanic_child = as.factor(hispanic),
         race_child = as.factor(race),
         age_child_nov = as.character(agenov1)) %>% 
  select(child_id_num, home_id, child_id_char, hispanic_child,
         race_child, age_child_nov, enrolled)

ak_home_initial <- read_xlsx("Input/AK/ak_home_20191216.xlsx") %>% 
  rename_all(tolower) %>% 
  select(homeid, home, txcondition) %>% 
  mutate(home_id = as.character(homeid),
         home = as.character(home),
         treatment = as.factor(txcondition)) %>% 
  select(home_id, home, treatment)

ak_homewinter_initial <- read_xlsx("Input/AK/ak_homewinter_20191216.xlsx") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, homeid, winterid, interventiondate, interventiontime) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         home_id = as.character(homeid),
         winter_id = as.character(winterid),
         intervention_date = interventiondate,
         intervention_time = interventiontime) %>% 
  select(home_winter_id, home_id, winter_id, intervention_date, intervention_time)

ak_parent_demographics_initial <-
  read_xlsx("Input/AK/ak_parent_demographics_20191216.xlsx") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, gender, hispanic, race, income, education,
         totalres, underfive) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         gender_parent = as.factor(gender),
         hispanic_parent = as.factor(hispanic),
         race_parent = as.factor(race),
         income = as.factor(income),
         education = as.factor(education),
         total_residents = as.character(totalres),
         residents_under_five = as.character(underfive)) %>% 
  select(home_winter_id, gender_parent, hispanic_parent, race_parent,
         income, education, total_residents, residents_under_five) %>% 
  filter(!is.na(gender_parent))

>>>>

---
title: "KidsAIR initial home/child data work"
author: "Ethan Walker"
date: "Started 19 Nov 2019, Updated 17 Dec 2019"
output: pdf_document
---

@@

# Load, format, and save home and child overview/demographic data for WMT
```{r}
# Load files
## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > WMT > child.xlsx
wmt_child_initial <- read_xlsx("Input/WMT/wmt_child_20191126.xlsx") %>% 
  rename_all(tolower) %>% 
  select(childid, homeid, id, hispanic, race, agenov1, enrolled) %>% 
  mutate(child_id_num = as.character(childid),
         home_id = as.character(homeid),
         child_id_char = as.character(id),
         hispanic_child = as.factor(hispanic),
         race_child = as.factor(race),
         age_child_nov = as.character(agenov1)) %>% 
  select(child_id_num, home_id, child_id_char, hispanic_child,
         race_child, age_child_nov, enrolled)

## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > WMT > home.xlsx
wmt_home_initial <- read_xlsx("Input/WMT/wmt_home_20191126.xlsx") %>% 
  rename_all(tolower) %>% 
  select(homeid, home, txcondition) %>% 
  mutate(home_id = as.character(homeid),
         home = as.character(home),
         treatment = as.factor(txcondition)) %>% 
  select(home_id, home, treatment)

## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > WMT > homewinter.xlsx
wmt_homewinter_initial <- read_xlsx("Input/WMT/wmt_homewinter_20191126.xlsx") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, homeid, winterid, interventiondate, interventiontime) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         home_id = as.character(homeid),
         winter_id = as.character(winterid),
         intervention_date = interventiondate,
         intervention_time = interventiontime) %>% 
  select(home_winter_id, home_id, winter_id, intervention_date, intervention_time)

## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > WMT > Home Data > parentdemographics.xlsx
wmt_parent_demographics_initial <-
  read_xlsx("Input/WMT/wmt_parent_demographics_20191126.xlsx") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, gender, hispanic, race, income, education,
         totalres, underfive) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         gender_parent = as.factor(gender),
         hispanic_parent = as.factor(hispanic),
         race_parent = as.factor(race),
         income = as.factor(income),
         education = as.factor(education),
         total_residents = as.character(totalres),
         residents_under_five = as.character(underfive)) %>% 
  select(home_winter_id, gender_parent, hispanic_parent, race_parent,
         income, education, total_residents, residents_under_five) %>% 
  filter(!is.na(gender_parent))

@@

# Load, format, and save home and child overview/demographic data for NN
```{r}
# Load files
## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > Navajo > child.xlsx
nn_child_initial <- read_xlsx("Input/NN/nn_child_20191216.xlsx") %>% 
  rename_all(tolower) %>% 
  select(childid, homeid, id, hispanic, race, agenov1, enrolled) %>% 
  mutate(child_id_num = as.character(childid),
         home_id = as.character(homeid),
         child_id_char = as.character(id),
         hispanic_child = as.factor(hispanic),
         race_child = as.factor(race),
         age_child_nov = as.character(agenov1)) %>% 
  select(child_id_num, home_id, child_id_char, hispanic_child,
         race_child, age_child_nov, enrolled)

## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > Navajo > home.xlsx
nn_home_initial <- read_xlsx("Input/NN/nn_home_20191216.xlsx") %>% 
  rename_all(tolower) %>% 
  select(homeid, home, txcondition) %>% 
  mutate(home_id = as.character(homeid),
         home = as.character(home),
         treatment = as.factor(txcondition)) %>% 
  select(home_id, home, treatment)

## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > Navajo > homewinter.xlsx
nn_homewinter_initial <- read_xlsx("Input/NN/nn_homewinter_20191216.xlsx") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, homeid, winterid, interventiondate, interventiontime) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         home_id = as.character(homeid),
         winter_id = as.character(winterid),
         intervention_date = interventiondate,
         intervention_time = interventiontime) %>% 
  select(home_winter_id, home_id, winter_id, intervention_date, intervention_time)

## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > Navajo > Home Data > parentdemographics.xlsx
nn_parent_demographics_initial <-
  read_xlsx("Input/NN/nn_parent_demographics_20191216.xlsx") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, gender, hispanic, race, income, education,
         totalres, underfive) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         gender_parent = as.factor(gender),
         hispanic_parent = as.factor(hispanic),
         race_parent = as.factor(race),
         income = as.factor(income),
         education = as.factor(education),
         total_residents = as.character(totalres),
         residents_under_five = as.character(underfive)) %>% 
  select(home_winter_id, gender_parent, hispanic_parent, race_parent,
         income, education, total_residents, residents_under_five) %>% 
  filter(!is.na(gender_parent))

@@

# Load, format, and save home and child overview/demographic data for AK
```{r}
# Load files
## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > AK > child.xlsx
ak_child_initial <- read_xlsx("Input/AK/ak_child_20191216.xlsx") %>% 
  rename_all(tolower) %>% 
  select(childid, homeid, id, hispanic, race, agenov1, enrolled) %>% 
  mutate(child_id_num = as.character(childid),
         home_id = as.character(homeid),
         child_id_char = as.character(id),
         hispanic_child = as.factor(hispanic),
         race_child = as.factor(race),
         age_child_nov = as.character(agenov1)) %>% 
  select(child_id_num, home_id, child_id_char, hispanic_child,
         race_child, age_child_nov, enrolled)

## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > AK > home.xlsx
ak_home_initial <- read_xlsx("Input/AK/ak_home_20191216.xlsx") %>% 
  rename_all(tolower) %>% 
  select(homeid, home, txcondition) %>% 
  mutate(home_id = as.character(homeid),
         home = as.character(home),
         treatment = as.factor(txcondition)) %>% 
  select(home_id, home, treatment)

## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > AK > homewinter.xlsx
ak_homewinter_initial <- read_xlsx("Input/AK/ak_homewinter_20191216.xlsx") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, homeid, winterid, interventiondate, interventiontime) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         home_id = as.character(homeid),
         winter_id = as.character(winterid),
         intervention_date = interventiondate,
         intervention_time = interventiontime) %>% 
  select(home_winter_id, home_id, winter_id, intervention_date, intervention_time)

## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > AK > Home Data > parentdemographics.xlsx
ak_parent_demographics_initial <-
  read_xlsx("Input/AK/ak_parent_demographics_20191216.xlsx") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, gender, hispanic, race, income, education,
         totalres, underfive) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         gender_parent = as.factor(gender),
         hispanic_parent = as.factor(hispanic),
         race_parent = as.factor(race),
         income = as.factor(income),
         education = as.factor(education),
         total_residents = as.character(totalres),
         residents_under_five = as.character(underfive)) %>% 
  select(home_winter_id, gender_parent, hispanic_parent, race_parent,
         income, education, total_residents, residents_under_five) %>% 
  filter(!is.na(gender_parent))
